Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-06 ms.tex
still working on goodness-of-fit section

The posterior sampling framework thus far described also affords us an 
opportunity to cross-check the conclusions of the correlation slope analysis in
$\S$\ref{sec:global}. The basic idea will be to continue sampling the posterior
of Equation \ref{eqn:post}, but at low resolution ($N_{side}$=64), including 
all HFI bands as well as DIRBE 100$\mu$m, 140$\mu$m and 240$\mu$m, and 
switching to a uniform prior on $T_2$. Under these circumstances, the 
chi-squared corresponding to the best-fit parameters for each pixel, termed 
$\chi^2_p$, is simply $-2 \times log(P_{max})$. 
% maybe invent a term chi^2_p or something to 
% reduce potential confusion caused by notation

@@

Because we seek to compare the goodness-of-fit for various dust SED models in 
the diffuse ISM, we restrict to a set of $\sim$10,800 pixels ($\sim$22\% of the
sky), with $|b|>30^{\circ}$ and $|\beta|>10^{\circ}$. We also avoid the SMICA 
inpainting mask, pixels with appreciable CO contamination, and compact sources.
The goodness-of-fit `objective function' we employ to judge the quality of 
a particular dust SED model is $\langle \chi^2_p \rangle$, where the average 
is taken over the aforementioned set of $\sim$10,800 pixels. 
$\langle \chi_{p}^2 \rangle$ is also equivalent to the reduced chi-squared, 
$\chi^2_{\nu}$, when considering the total number of free parameters to be the 
number of pixels multiplied by the number of free parameters per pixel, and 
similarly for the total number of constraints.

We calculate $\chi^2_{\nu}$ for various dust SED models, independently 
minimizing each $\chi^2_p$ by finding pixel $p$'s best-fitting dust 
temperature and normalization, then evaluating $\langle \chi_{p}^2 \rangle$. 
First, we consider single-MBB models with $\beta$ spatially constant (see the
black line in Figure \ref{fig:chi2_dirbe}). $\beta$=1.57 yields the best fit, 
with $\chi^2_{\nu}$=2.51. This result is in excellent agreement with that of 
$\S$\ref{sec:global}, where we found the best-fit single-MBB model to have 
$\beta$=1.59. We also evaluated $chi^2_{\nu}$ for single-MBB models in which
$\beta$ varies spatially. In these cases, we used the $\beta$ map from 
\cite{planckdust}. We started by calculating $\chi^2_{\nu}$ using the 
\cite{planckdust} temperature map, finding $chi^2_{\nu}$=4.68. Note that
in this case no per-pixel chi-squared minimization was involved, as we simply 
evaluated $\chi^2_{p}$ for each pixel based on the fully-specified 
\cite{planckdust} model. % mention beta template but floating t, normalization

% mention other single MBB variants

>>>>

The posterior sampling framework thus far described also affords us an
opportunity to evaluate the goodness-of-fit for competing dust SED models, and 
thereby cross-check the conclusions of our correlation slope analysis in
$\S$\ref{sec:global}. The basic idea will be to continue sampling the posterior
of Equation \ref{eqn:post}, but at low resolution ($N_{side}$=64), including 
all HFI bands as well as DIRBE 100$\mu$m, 140$\mu$m and 240$\mu$m, and 
switching to a uniform prior on $T_2$. Under these circumstances, the 
chi-squared corresponding to the best-fit parameters for each pixel, termed 
$\chi^2_p$, is simply $-2 \times log(P_{max})$. We will refer to the
per-pixel chi-squared per degree of freedom as $\chi^2_{p, \nu}$
% maybe invent a term chi^2_p or something to 
% reduce potential confusion caused by notation

@@

Because we seek to compare the goodness-of-fit for various dust SED models in 
the diffuse ISM, we restrict to a set of $\sim$10,800 pixels ($\sim$22\% of the
sky), with $|b|>30^{\circ}$ and $|\beta|>10^{\circ}$. We also avoid the SMICA 
inpainting mask, pixels with appreciable CO contamination, and compact sources.
The goodness-of-fit `objective function' we employ to judge the quality of 
a particular dust SED model is $\langle \chi^2_{p, \nu} \rangle$, where the 
average is taken over the aforementioned set of $\sim$10,800 pixels. 
$\langle \chi_{p, \nu}^2 \rangle$ is also equivalent to the reduced 
chi-squared, $\chi^2_{\nu}$, when considering the total number of free 
parameters to be the number of pixels multiplied by the number of free 
parameters per pixel (and similarly for the total number of constraints), and
taking $\chi^2$=$\sum\chi^2_{p}$.

We calculate $\chi^2_{\nu}$ for various dust SED models, independently 
minimizing each $\chi^2_p$ by finding pixel $p$'s best-fitting dust 
temperature and normalization, then evaluating $\langle \chi_{p}^2 \rangle$. 
First, we consider single-MBB models with $\beta$ spatially constant (see the
black line in Figure \ref{fig:chi2_dirbe}). $\beta$=1.57 yields the best fit, 
with $\chi^2_{\nu}$=2.51. This result is in excellent agreement with that of 
$\S$\ref{sec:global}, where we found the best-fit single-MBB model to have 
$\beta$=1.59.

We also evaluated $\chi^2_{\nu}$ for single-MBB models in which
$\beta$ varies spatially. In these cases, we adopted the 0.5$^{\circ}$ 
resolution $\beta$ map from \cite{planckdust}. We started by calculating 
$\chi^2_{\nu}$ using the \cite{planckdust} temperature map, finding 
$\chi^2_{\nu}$=4.68. Note that in this case no per-pixel chi-squared 
minimization was involved, as we simply evaluated $\chi^2_{p}$ for each pixel 
based on the fully-specified \cite{planckdust} emission model. Next, we tested 
a single-MBB model for which we adopted the \cite{planckdust} $\beta$ map, but 
allowed the per-pixel temperature and normalization to vary so as to minimize 
$\chi^2_p$. In this case, we found $\chi^2_{\nu}$=2.51, effectively identical 
to the value found for the spatially constant $\beta$=1.57 single-MBB model. 
This is perhaps unsurprising, as the average $\beta$ value from 
\cite{planckdust} over the mask in question is $\langle\beta\rangle$=1.58. 
This result does suggest, however, that the half-degree variations in $\beta$ 
are not materially improving the goodness-of-fit over the full frequency range 
100-3000 GHz relative to a model with appropriately chosen spatially constant 
$\beta$.

% mention that when t floats, we find a lower T than the Planck team?
% mention beta template but floating t, normalization
